\cvsection{Work Experience}
\begin{cventries}

    \cventry
    {POS Android Developer}
    {Payoo}
    {Ho Chi Minh City, Vietnam}
    {August.2024 -- Present}
    {
        \begin{cvitems}
            \item {
                Extended support from one promotion per transaction to multiple promotions with different types.
                Wrote advanced validations, groupings, and error handling for promotion combinations.
            }
            \item {
                Developed partner support feature to create and continue payment for draft orders, supporting full order flow: session connect/start/end,
                multi-option selections, multiple promotions, and multiple payment methods per order. Handled edge cases involving transaction result
                mismatches between payment systems and partner systems.
            }
            \item {
                Developed multi-module order feature with product listing, category header items, tabs, dropdown filters, and order summary;
                designed as a configurable and reusable component adaptable across multiple merchants with varying product data.
            }
            \item {
                Fixed rare but critical transaction mismatch bug between POS and store devices in link mode;
                identified handshake protocol issues and hardened flow to ensure cross-system consistency.
            }
        \end{cvitems}
    }

    \cventry
    {Android Developer}
    {Be Earning JSC}
    {Ho Chi Minh City, Vietnam}
    {March.2024 -- July.2024}
    {
        \begin{cvitems}
            \item {
                Develope launcher feature to manage user apps alongside enterprise web apps.
            }
            \item {
                Leverage system services to overlay system layouts and manage notification data, including controlling current music service.
                Implement foreground service to draw overlay custom draggable components(including camera) or in-app elements based on context.
            }
            \item {
                Create permission manager to dynamically check run-time and special permissions, including permission chains, exposing checks as Flows for reactive handling.
                Separate business logic into use cases from UI layer to facilitate sharing between activities and services.
            }
            \item {
                Address memory leaks, incorrect context usage, and improve UI thread performance by running slow calls and disk accesses on appropriate dispatchers using LeakCanary and StrictMode.
            }
        \end{cvitems}
    }

    \cventry
    {Android Developer}
    {EnglishWing Vietnam}
    {Ho Chi Minh City, Vietnam}
    {June.2023 -- Sep.2023}
    {
        \begin{cvitems}
            \item {
                Develope Android app connected to Supabase Realtime for admin users to manage real-time user information and update latest class time in user app.
                Implement preloading data and real-time channels during SplashScreen state.
                Adapt time display based on device timezone using receivers.
            }
            \item {
                Develope virtual pet app.
                Implement pet room for chat by text or voice and sending gifts to increase intimacy.
                Created various Compose animations (shimmer, droplet, flashcard, etc.).
                Set up interceptors for internet connectivity checks and authentication headers.
            }
        \end{cvitems}
    }

    \cventry
    {Xamarin Android Developer}
    {CloudConnectTech}
    {Ho Chi Minh City, Vietnam}
    {Dec.2020 -- June.2021}
    {
        \begin{cvitems}
            \item {
                Enhance purchase feature in Fintech app for POS machine.
                Update UI, SQLite database and business logic to align with new flow.
                Update receipt printing function.
            }
            \item {
                Develope attendance app for employees with features to create and edit profiles using facial data,
                check-in and check-out via facial recognition,
                and view attendance history.
            }
        \end{cvitems}
    }

    \cventry
    {Mobile Developer, Intern}
    {TMA Solutons}
    {Ho Chi Minh City, Vietnam}
    {Sep.2020 -- Dec.2020}
    {
        \begin{cvitems}
            \item {
                Implement UI using UIKit and navigation for iOS VPN app.
                Customize UI components such as dropdown menus and UITextField displaying validation messages.
            }
        \end{cvitems}
    }

\end{cventries}
