\cvsection{Personal Project}
\begin{cventries}

    \cventry
    {\href{https://github.com/neronguyenvn/Reorderable-Launcher}{GitHub}}
    {Reorderable Launcher}
    {}{}
    {
        \begin{cvitems}
            \item {
                Develope Android Composable launcher app, implement dynamic grid layout allowing apps to be auto-arranged as they are dragged within grid.
            }
            \item {
                Utilize RoomDB to store app position indexes and page indexes, ensuring asynchronous updates to app positions in both data and UI layers.
            }
        \end{cvitems}
    }

    \cventry
    {\href{https://github.com/neronguyenvn/decor-assistant-app}{GitHub}}
    {Decor Assistant App}
    {}{}
    {
        \begin{cvitems}
            \item {
                Develop Android decor assistant app.
                Users can take new photo or select image to receive room decor suggestions from Gemini.
            }
        \end{cvitems}
    }

    \cventry
    {\href{https://github.com/neronguyenvn/firebase-auth-chat-app}{App} | \href{https://github.com/neronguyenvn/firebase-auth-chat-server}{Server}}
    {Chat App}
    {}{}
    {
        \begin{cvitems}
            \item {
                Develop Android chat app and server with Ktor Server.
                Implement Google Sign-in, verify JWT with Firebase Auth and Admin.
            }
            \item {
                Connect authenticated users to shared chat room and show chat history.
                Push notifications to users for new messages.
            }
            \item {
                Save user infomation and user messages on server with MongoDB Atlas.
                Offer offline-first chat history in app with Realm.
            }
        \end{cvitems}
    }

    \cventry
    {\href{https://github.com/neronguyenvn/kmp-graphql-country-app}{GitHub}}
    {Country App}
    {}{}
    {
        \begin{cvitems}
            \item {
                Develop Compose Multiplatform country list app for Desktop, Android.
                Make GraphQL requests with Appolo Kotlin.
            }
        \end{cvitems}
    }

    \cventry
    {\href{https://github.com/neronguyenvn/clean-architecture-weather-app}{GitHub} | \href{https://play.google.com/store/apps/details?id=com.nero.weatherjourney}{Google Play}}
    {Weather App}
    {}{}
    {
        \begin{cvitems}
            \item {
                Develop Android weather forecast app.
                Cache previously shown city and favorite cities.
                Implement setting menu for select weather units.
            }
            \item {
                Implement network monitor to notify and resend requests.
                Send requests concurrently with Kotlin Channel for better performance.
            }
        \end{cvitems}
    }
\end{cventries}
